Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-06 analysis/paper/paper.Rmd
Move the loading of the model objects

theme_set(theme_classic())
```

@@

load(system.file("extdata",
            "m_k1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_k2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))

>>>>

theme_set(theme_classic())

load(system.file("extdata",
            "m_k1.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
load(system.file("extdata",
            "m_k2.Rda",
            package = "Reproducibility.in.Plant.Pathology",
            mustWork = TRUE))
```

@@
